The Evolution of Phenotypically Invariant Genetic Networks

### 2021-08-16 review-responses2.tex

%%%%%%
%%
%%  Don't reorder the reviewer points; that'll mess up the automatic referencing!
%%
%%%%%

%\begin{minipage}[b]{2.5in}
%  Revision Cover Letter \\
%  {\it Evolution}
%\end{minipage}
%\hfill
%\begin{minipage}[b]{2.5in}
%    Joshua Schiffman \\
%    \emph{and} Peter Ralph \\
%  \today
%\end{minipage}
% 
%\vskip 2em
% 
%\noindent
%{\bf To the Editor(s) -- }
% 
%\vskip 1em
%
%We are writing to submit a revision of our manuscript, ``{System drift and speciation}'' (ID 21-0262), for your review.
%We would like to thank you and the reviewers for your enthusiasm
%and your suggestions -- they have helped us improve our manuscript's accuracy and clarity.
%
%Both reviewers made comments about the section on Haldane's rule, which we have revised accordingly.
%We also made an effort to provide more context for our manuscript by citing the additional literature, as requested by Reviewer 1. 
%To address some of Reviewer 2's concerns, we added more discussion and detail pertaining to system theory and its biological interpretation.
%
%Line numbers in the response to reviewers refer to the revised document;
%in addition we are submitting a color-coded pdf showing differences to the previous submission
%that has its own copy of the review responses at the end (and line number references are consistent within this file as well).
%
%We hope that you enjoy the resulting manuscript as much as we do.
% 
%
%\vskip 5em
%
%\noindent \hspace{4em}
%\begin{minipage}{3in}
%\noindent
%{\bf Sincerely,}
%
%\vskip 2em
%
%{\bf 
%Joshua Schiffman and
%Peter Ralph
%}\\
%\end{minipage}
%
%\vskip 4em
%
%\pagebreak
%
%%%%%%%%%%%%%%
\reviewersection{AE}
\begin{quote}
This is a very interesting theory paper that connects the modeling and evolution of regulatory networks with speciation. While quite theoretical in nature, the authors made an effort to provide examples, and I consider this paper of very high relevance for the field.

### 2021-08-16 kalman_walk_paper.tex
edits for submission

\section*{Acknowledgements}

We would like to thank Sergey Nuzhdin, Stevan Arnold, Michael Turelli, Patrick Phillips, Erik Lundgren and Hossein Asgharian for valuable discussion. 
We would also like to thank Nick Barton, Sarah Signor, Todd Parsons, and Joachim Hermisson for very helpful comments on the manuscript.
Work on this project was supported by funds from
the Sloan Foundation and the NSF (under DBI-1262645) to PR.

>>>>

%\section*{Acknowledgements}
%
%We would like to thank Sergey Nuzhdin, Stevan Arnold, Michael Turelli, Patrick Phillips, Erik Lundgren and Hossein Asgharian for valuable discussion. 
%We would also like to thank Nick Barton, Sarah Signor, Todd Parsons, and Joachim Hermisson for very helpful comments on the manuscript.
%Work on this project was supported by funds from
%the Sloan Foundation and the NSF (under DBI-1262645) to PR.
%
